% (c) 2009-2016 by Markus Leupold-Löwenthal
% This file is released under CC BY-SA 4.0. Please do not apply one-way compatible licenses.

\renewcommand{\flyerVersion}{v0.1}

% CHANGELOG-en
%
% v0.1
%   - first version

% --- language dependent typography stuff --------------------------------------

\renewcommand{\say}[1]{“\textit{#1}”}
\setdefaultlanguage{english}

\renewcommand{\fsNormal}{\fontsize{11pt}{13.2pt plus 0pt minus 0pt}}
%\renewcommand{\fsSmall}{\fontsize{9pt}{10pt plus 0.1pt minus 0pt}}

% --- pdf metadata -------------------------------------------------------------

\hypersetup{
	pdfsubject={A NIP'AJIN RPG on a flyer.},
}

% --- front page ---------------------------------------------------------------

\renewcommand{\rulesTitle}{%
	\noindent\color{primary}%\fontsize{10.5mm}{12mm}\selectfont%
	\makebox[\linewidth][l]{\spaceout{PLAY ME -- I AM A}} \par%
	\noindent\color{white}%\fontsize{10.5mm}{12mm}\selectfont%
	\makebox[\linewidth][l]{\fffancy\spaceout{LEAFLET RPG!}} \par%
}

\renewcommand{\rulesHeadline}{Rules}

\renewcommand{\rulesText}{%

	\noindent
	This leaflet contains an abridged version of \keyword{NIP'AJIN}, a free and universal pen-and-paper role playing game.

	\bigskip

	\noindent
	Your \keyword{character} needs a d4, d6, d8, d10 and d12. One of those you designate as \keyword{hit die} \HD\ and put it, highest number up, on the table. If this die ever is reduced below 1, your character is \keyword{overcome} and drops out of the game. The remaining four dice are your \keyword{available dice}.

	When the (timely) outcome of a task is unclear, pick an \keyword{action die} \AD\ from your available dice. Roll it, and if nobody opposes you, the task succeeds if you \keyword{roll four or higher}.

	If your want to attack opponents, their players have to choose a \keyword{reaction die} \RD from their available die and roll them, too. If your \AD gets an higher result than the \RD, your attack was successful -- even if it shows less than four. Your opponent’s \HD\ then drops by 1.

	After each roll, the used \AD/\RD\ are \keyword{exhausted} and placed aside. Once all your character's dice are exhausted, they become available again.

	\bigskip

	\hfill Now play the scenario on the other side!
}

\renewcommand{\rulesURL}{\href{http://ludus-leonis.com/en/nipajin}{LUDUS-LEONIS.COM/en}}

% --- back page ----------------------------------------------------------------
\renewcommand{\settingTitle}{%
	\noindent\color{primary}\fontsize{5mm}{6mm}\selectfont% , and that day may never come,
	\makebox[\linewidth][l]{\spaceout{Someday, and that day may never}} \par%
	\noindent\color{primary}\fontsize{5mm}{6mm}\selectfont% , and that day may never come,
	\makebox[\linewidth][l]{\spaceout{come, I'll call upon you to play this}} \par%
	\noindent\color{white}\fontsize{12.5mm}{11mm}\selectfont%
	\makebox[\linewidth][l]{\fffancy\spaceout{LEAFLET RPG!}} \par%
}

\renewcommand{\settingHeadline}{Scenario: Small Fry}

\renewcommand{\settingText}{%
	\noindent
	This scenario for 2 to 6 characters uses the rules from the other side.

	Decide upon a city, a criminal organization and a time period, for example the Mafia in New York during the 1950s or Yakuza in contemporary Osaka. Your characters are \keyword{petty crooks}, forced to work as a group by the local \keyword{Big Boss} -- the Game Master. Each character is named and described briefly and uses the d4 as \HD. During the game, you try to outrival and overcome the other characters to become the right-hand man of the Big Boss.

	The game takes place over several episodes that span a week each. Each episode, the Big Boss assigns a job the group, for example a heist, an abduction, or collecting protection money. It doesn't matter if those jobs succeed, but they set the stage on which the characters compete with each other. Each episode, each player can attempt to harm one other character and reduce his \HD\ by 1. Overcome characters leave the city at the end of the week.

	Once per game, if you feel treated unfairly in an episode, you may visit the Big Boss to \keyword{ask for a favour}. Pick a \AD, and if you roll 4+, your plea was heard. The Big Boss sends his goons to beat everyone up that harmed your character this episode (-2 on their \HD). If your fail that roll, your character gets beaten up instead.

}

\renewcommand{\settingURL}{\href{http://ludus-leonis.com/nipajin}{LUDUS-LEONIS.COM}}
