% (c) 2009-2016 by Markus Leupold-Löwenthal
% This file is released under CC BY-SA 4.0. Please do not apply one-way compatible licenses.

% CHANGELOG-en
%
% v1.0.1
%   - start of changelog

\renewcommand{\rulesVersion}{v1.0.1}

% --- front page ---------------------------------------------------------------

\renewcommand{\rulesTitle}{\fontsize{12.5mm}{12mm}\selectfont

	\noindent\color{primary}\addfontfeature{WordSpace=1.6,LetterSpace=4.0}
		PLAY ME -- I AM A

	\noindent\color{white}\fffancy\fontsize{12.5mm}{12mm}\selectfont\addfontfeature{WordSpace=2,LetterSpace=12.0}
		LEAFLET RPG!

}

\renewcommand{\rulesHeadline}{Rules}

\renewcommand{\rulesText}{%

	\noindent
	This leaflet contains an abridged version of \keyword{NIP'AJIN}, a free and universal pen-and-paper role playing game.

	\bigskip

	\noindent
	Your \keyword{character} needs a d4, d6, d8, d10 and d12. One of those you designate as \keyword{hit die} \HD\ and put it, highest number up, on the table. If this die ever is reduced below 1, your character is \keyword{overcome} and drops out of the game. The remaining four dice are your \keyword{available dice}.

	When the (timely) outcome of your character's task is unclear, you have to pick an \keyword{action die} \AD\ from your available dice. Roll it. The task succeeds on a \keyword{roll of four or higher}, if nobody opposes you.

	If your character meets with resistance, the opposing players pick a \keyword{reaction die} \RD\ from their available dice. If your \AD\ rolls equal or higher than the \RD, you win -- even if it results in less than four. If this was an attack, your opponent’s \HD\ drops by 1.

	After each roll, the used \AD/\RD\ are \keyword{exhausted} and placed aside. Once all your character's dice are exhausted, they become available again.

	\bigskip

	\hfill Now you can play the scenario on the other side!
}

\renewcommand{\rulesURL}{\href{https://ludus-leonis.com/en}{ludus-leonis.com/en}}
